Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-24 DGMM2025/paper.tex
refs
added octaflower images and kernel specifications for normals

\usepackage{changes}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{varwidth}
\usepackage{mathtools}
\usepackage{pgfplots}
\usepackage[dvipsnames]{xcolor}
\pgfplotsset{compat=1.18}
\usetikzlibrary {spy,arrows.meta,decorations.shapes}
\setauthormarkup{}
\definechangesauthor[name=jo, color=blue]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
    coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
    of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
    visible using the same method as presented in~\ref{fig:visibility-algorithm-evolution}.

@@

    \begin{figure}
        \centering
        \begin{tabular}{c c}
            \includegraphics[width=0.4\textwidth]{pictures/visibility_from_given_point_r_10} &
            \includegraphics[width=0.4\textwidth]{pictures/visibility_aware_of_features}
        \end{tabular}
        \caption{Examples of visibility on a fandisk and a torus knot. First one is on the edge
        of a fandisk, where the visibility stops at the edges. The other one is in the interior
        of a torus knot, where we can see that the visibility is feature-aware and doesn't see
        the other side of the torus' branch.}
        \label{fig:visibility-examples}
    \end{figure}
%
%    \begin{figure}
%        \begin{center}
%            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
%            \caption{Visibility of a point on an edge of a fandisk}
%            \label{fig:visibility-fandisk}
%        \end{center}
%    \end{figure}
%    \begin{figure}
%        \begin{center}
%            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
%            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
%            \label{fig:visibility-torus-knot}
%        \end{center}
%    \end{figure}

@@

    \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
    \paragraph{Saliency-aware normal estimator.}
    We propose a new normal estimator on digital surfaces, which uses
    the visibility of the point of interest while taking into account
    a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
    average length between visible points (so some
    $\Theta(\sqrt{h})$), then this estimator is observed to be
    multigrid convergent along digitization of smooth shapes. However,
    since the computation window is limited by the visibility, it
    better approximates the geometry near sharp or salient features.

@@

    \begin{figure}
        \centering
        \begin{tabular}{|c||c|c|}
            \hline
            II normals &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
            \hline
            Visibility normals &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
            \hline
        \end{tabular}
        \caption{Examples of normals computed on a chinese dragon as a
          color map. First set displays II normals, second set uses
          the visibility algorithm to compute them. The normals are
          colored according to their orientation as $0.5 \cdot (n_i +
          \mathbbm{1})$. The right images are the smooth version of
          the left images}
        \label{fig:normals-estimation}
    \end{figure}

@@

    \begin{figure}
        \begin{center}
            \begin{tabular}{|c||c|c|c|}
                \hline
                Curv. & II normals & CTriv normals & Our normals \\ \hline \hline
                \raisebox{18mm}{$\kappa_1$} &
                \MyZoom{pictures/d20-k1-II.jpg} &
                \MyZoom{pictures/d20-k1-CTriv.jpg}&
                \MyZoom{pictures/d20-k1-VN.jpg}\\ \hline
                \raisebox{18mm}{$\kappa_2$} &
                \MyZoom{pictures/d20-k2-II.jpg} &
                \MyZoom{pictures/d20-k2-CTriv.jpg}&
                \MyZoom{pictures/d20-k2-VN.jpg}\\ \hline
                \raisebox{18mm}{$H$} &
                \MyZoom{pictures/d20-H-II.jpg} &
                \MyZoom{pictures/d20-H-CTriv.jpg}&
                \MyZoom{pictures/d20-H-VN.jpg}\\ \hline
                \raisebox{18mm}{$G$} &
                \MyZoom{pictures/d20-G-II.jpg} &
                \MyZoom{pictures/d20-G-CTriv.jpg}&
                \MyZoom{pictures/d20-G-VN.jpg}\\ \hline
            \end{tabular}
        \end{center}
        \caption{\label{fig-curvatures}Estimation of curvatures using
          Corrected Normal Current estimators \cite{lachaud:2022-dcg}
          with a measure of radius $2$ for the shape ``Dice-20'' of
          Thingi10K database at resolution $256^3$. This estimator is
          parameterized by an input normal estimator: first column by
          ``Integral Invariant normals'' (radius $r=6$, second column
          by ``Convolved Trivial normals'' (radius $k=6$), third
          column by our presented normal estimator (deviation
          $\sigma=4$, radius $r=2\sigma=8$). Per row are displayed the
          estimated curvatures in order: first and second principal
          curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
          Gaussian curvature $G$. The range of curvature between deep
          blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
          color equal to $0$.}
    \end{figure}

>>>>

\usepackage{changes}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{varwidth}
\usepackage{mathtools}
\usepackage{pgfplots}
\usepackage[dvipsnames]{xcolor}
\usepackage[utf8]{inputenc}
\pgfplotsset{compat=1.18}
\usetikzlibrary {spy,arrows.meta,decorations.shapes}
\setauthormarkup{}
\definechangesauthor[name=jo, color=blue]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
    coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
    of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
    visible using the same method as presented in~\ref{fig:visibility-algorithm-evolution}. Some results of visible
    points are present in figure~\ref{fig:visibility-results}.

@@

    \begin{figure}
        \centering
        \begin{tabular}{c c}
            \includegraphics[width=0.4\textwidth]{pictures/visibility_from_given_point_r_10} &
            \includegraphics[width=0.4\textwidth]{pictures/visibility_aware_of_features}
        \end{tabular}
        \caption{Examples of visibility on a fandisk and a torus knot. First one is on the edge
        of a fandisk, where the visibility stops at the edges. The other one is in the interior
        of a torus knot, where we can see that the visibility is feature-aware and doesn't see
        the other side of the torus' branch.}
        \label{fig:visibility-results}
    \end{figure}
%
%    \begin{figure}
%        \begin{center}
%            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
%            \caption{Visibility of a point on an edge of a fandisk}
%            \label{fig:visibility-fandisk}
%        \end{center}
%    \end{figure}
%    \begin{figure}
%        \begin{center}
%            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
%            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
%            \label{fig:visibility-torus-knot}
%        \end{center}
%    \end{figure}

@@

    \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}

    \paragraph{Saliency-aware normal estimator.}
    We propose a new normal estimator on digital surfaces, which uses
    the visibility of the point of interest while taking into account
    a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
    average length between visible points (so some
    $\Theta(\sqrt{h})$), then this estimator is observed to be
    multigrid convergent along digitization of smooth shapes. However,
    since the computation window is limited by the visibility, it
    better approximates the geometry near sharp or salient features.

@@

    \begin{figure}
        \centering
        \begin{tabular}{|c||c|c||c|c|}
            \hline
            II normals &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
            \hline
            Visibility normals &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
            \hline
        \end{tabular}
        \caption{Examples of normals computed on a chinese dragon, then on an
        octaflower as a color map. First set displays II normals, second set
        uses the visibility algorithm to compute them. The normals are colored
        according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$. The
        right images are the smooth version of the left images. ``Integral
        Invariant normals'' are computed using a radius of $r=3$, while
        our normal estimator are computed using a deviation of $\sigma=3$, and so
        a radius of $r=2\sigma=6$}
        \label{fig:normals-estimation}
    \end{figure}

@@

    \begin{figure}
        \begin{center}
            \begin{tabular}{|c||c|c|c|}
                \hline
                Curv. & II normals & CTriv normals & Our normals \\ \hline \hline
                \raisebox{18mm}{$\kappa_1$} &
                \MyZoom{pictures/d20-k1-II.jpg} &
                \MyZoom{pictures/d20-k1-CTriv.jpg}&
                \MyZoom{pictures/d20-k1-VN.jpg}\\ \hline
                \raisebox{18mm}{$\kappa_2$} &
                \MyZoom{pictures/d20-k2-II.jpg} &
                \MyZoom{pictures/d20-k2-CTriv.jpg}&
                \MyZoom{pictures/d20-k2-VN.jpg}\\ \hline
                \raisebox{18mm}{$H$} &
                \MyZoom{pictures/d20-H-II.jpg} &
                \MyZoom{pictures/d20-H-CTriv.jpg}&
                \MyZoom{pictures/d20-H-VN.jpg}\\ \hline
                \raisebox{18mm}{$G$} &
                \MyZoom{pictures/d20-G-II.jpg} &
                \MyZoom{pictures/d20-G-CTriv.jpg}&
                \MyZoom{pictures/d20-G-VN.jpg}\\ \hline
            \end{tabular}
        \end{center}
        \caption{\label{fig-curvatures}Estimation of curvatures using
          Corrected Normal Current estimators \cite{lachaud:2022-dcg}
          with a measure of radius $2$ for the shape ``Dice-20'' of
          Thingi10K database at resolution $256^3$. This estimator is
          parameterized by an input normal estimator: first column by
          ``Integral Invariant normals'' (radius $r=6$), second column
          by ``Convolved Trivial normals'' (radius $k=6$), third
          column by our presented normal estimator (deviation
          $\sigma=4$, radius $r=2\sigma=8$). Per row are displayed the
          estimated curvatures in order: first and second principal
          curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
          Gaussian curvature $G$. The range of curvature between deep
          blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
          color equal to $0$.}
    \end{figure}
